---
title: "Three Proposals"
subtitle: "Proposal"
format: html
editor: visual
---

```{r}
#| label: load-pkgs
#| message: false

library(tidyverse)
squirrel <- read_csv("data/2018_Central_Park_Squirrel_Census_-_Squirrel_Data.csv")
global_emissions <- read_csv("data/global_emissions.csv")
hatecrimes <- read_csv("data/NYPD_Hate_Crimes.csv")
```

# Data 1

## Introduction and data

-   Identify the source of the data.

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

-   Write a brief description of the observations.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

-   Identify the types of variables in your research question. Categorical? Quantitative?

## Literature

-   Find one published credible article on the topic you are interested in researching.

-   Provide a one paragraph summary about the article.

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

## Glimpse of data

```{r}
#| label: load-data-1

glimpse(squirrel)
```

# Data 2

## Introduction and data

-   Identify the source of the data. **The data set is from the CORGIS** **data set and was created by Sam Donald.**

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data). **Sam Donald is the creator of the data set and was created on** **9/23/2022.**

-   Write a brief description of the observations. **The observations compares various countries and regions in relation to overall emission trends.** **The data set also compares from what industry such as coal, gas, etc and how much each industry adds to a specific emission.**

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

-   Identify the types of variables in your research question. Categorical? Quantitative?

## Literature

-   Find one published credible article on the topic you are interested in researching.

-   Provide a one paragraph summary about the article.

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

## Glimpse of data

```{r}
#| label: load-data-2

glimpse(global_emissions)
```

# Data 3

## Introduction and data

-   Identify the source of the data.
**The source of the data from NYC Open Data platform, specifically provided by the Police Department (NYPD).**

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).
**This data is collected by Open Data which is a free public data published by trained New York City agencies and other partners, including NYPD (New York City Policy Department. This data was recently updated on February 1, 2023 but created on October 29, 2020. It was originally collected through the NYPD records and provided to NYC Open Data to be organized and dispersed for the benefit of public safety. **

-   Write a brief description of the observations.
**This dataset observes NYC Hate Crimes within certain Borough in New York City happening at a specific time. It in depth looks at how certain claims have bias motives and within certain offense categories.**

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

-   Identify the types of variables in your research question. Categorical? Quantitative?

## Literature

-   Find one published credible article on the topic you are interested in researching.

-   Provide a one paragraph summary about the article.

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

## Glimpse of data

```{r}
#| label: load-data-3

glimpse(hatecrimes)
```
