---
title: "Three Proposals"
subtitle: "Proposal"
format: html
editor: visual
---

```{r}
#| label: load-pkgs
#| message: false

library(tidyverse)
squirrel <- read_csv("data/2018_Central_Park_Squirrel_Census_-_Squirrel_Data.csv")
global_emissions <- read_csv("data/global_emissions.csv")
hatecrimes <- read_csv("data/NYPD_Hate_Crimes.csv")
```

# Data 1

## Introduction and data

-   Identify the source of the data.

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

-   Write a brief description of the observations.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

-   Identify the types of variables in your research question. Categorical? Quantitative?

## Literature

-   Find one published credible article on the topic you are interested in researching.

-   Provide a one paragraph summary about the article.

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

## Glimpse of data

```{r}
#| label: load-data-1

glimpse(squirrel)
```

# Data 2

## Introduction and data

-   Identify the source of the data.

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

-   Write a brief description of the observations.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

-   Identify the types of variables in your research question. Categorical? Quantitative?

## Literature

-   Find one published credible article on the topic you are interested in researching.

-   Provide a one paragraph summary about the article.

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

## Glimpse of data

```{r}
#| label: load-data-2

glimpse(global_emissions)
```

# Data 3

## Introduction and data

-   Identify the source of the data.

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

-   Write a brief description of the observations.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

    Research Question: In recent years, how have hate crime bias motives shifted in New York City?

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

Hate crimes in New York City is a research topic that examines the prevalence, location, date, offense description, and reason for bias-motivated incidents that occur in the city. A hate crime is a criminal act that is committed against an individual or group based on their perceived or actual race, ethnicity, religion, gender, sexual orientation, or other characteristics. This data set includes information on the bias-motive for these crimes; were they racially motivated(anti-Asian, anti-Black, etc), religiously motivated (anti-Jewish, etc), gender motivated (anti-female, anti-trans), sexually motivated (homosexual, etc), and more. We hypothesize that in the wake of the COVID-19 pandemic, anti-Asian hate crimes in New York City have increased.

-   Identify the types of variables in your research question. Categorical? Quantitative?

We are focusing on the variable "Bias Motive Description", which is a categorical variable.

## Literature

-   Find one published credible article on the topic you are interested in researching.

-   Provide a one paragraph summary about the article.

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

## Glimpse of data

```{r}
#| label: load-data-3

glimpse(hatecrimes)
```
