---
title: "Project: Global Emissions"
subtitle: "Report"
format: html
editor: visual
execute:
  echo: true
---

Project - Global Emissions

**- Introduction and data**

Climate change is one of the most pressing issues facing the world today, and global emissions are a major driver of this phenomenon. As human activities continue to release greenhouse gasses into the atmosphere, the Earth's temperature is rising at an unprecedented rate. Consequently, a host of negative consequences such as sea level rise, more frequent and severe weather events, and ecosystem disruption have risen. Fossil fuels are undoubtedly the largest contributor to global climate change. In fact fossil fuels, which include coal, oil and gas account for over 75 percent of global greenhouse gas emissions and nearly 90 per cent of all carbon dioxide emissions. Climate change is widely regarded as the biggest issue we will face; its far reaching effects on the environment and human society pose significant challenges for present and future generations. Considering greenhouse gasses, and consequently fossil fuels are the largest contributor to this acceleration, urgent action is required to reduce our reliance on these energy sources. For these reasons, we have decided to surface the unignorable climate change crisis by delving deeper into the issue of global emissions, particularly fossil fuel usage.

The research question being explored is "Which industry between coal, gas, and oil in India, China, and USA creates the most CO2 emission production from 1992 to 2018?" We have chosen to focus on these three countries as they are the top 3 contributors to global emissions. Together, China, the US, and India contribute to nearly half of the global greenhouse gas emissions. In 2019, China contributed 27%, the US contributed 11%, and India contributed 6.6%. The research question will look at these three specified countries and compare over time which industry (coal, gas or oil) in each country releases the most and least CO2 emission and if the industry adding the most CO2 to the atmosphere changes for each country over time. The hypothesis is that because the three countries are in different stages of development, India and China will have coal as the industry causing the most CO2 emission and USA will have oil as the industry emitting the most CO2.

To answer our research question we will be utilizing data from the CORGIS data set. The data set was created by Sam Donald, and was created on September 23, 2022. The observations of this data set compare various countries and regions in relation to overall emission trends. The data set also compares what industry such as coal, gas, etc is responsible for these emissions and how much each industry adds to a specific emission type. The variables from this data set that are involved in our research question are "Emissions.Production.CO2.Coal", "Emissions.Production.CO2.Gas", and "Emissions.Production.CO2.Oil" All of these variables are quantitative variables. Each row of the data represents a different country with a year between 1992 and 2018 in chronological order. The response variables in this research question are the amount of CO2 emissions produced by the coal, gas, and oil industries ("Emissions.Production.CO2.Coal", "Emissions.Production.CO2.Gas", and "Emissions.Production.CO2.Oil") in India, China, and the USA from 1992 to 2018. The variable is quantitative and continuous, as it measures the amount of CO2 emissions produced by each industry in each country over a period of time.

To our knowledge, there are not any glaring ethical concerns regarding the collection of this data. Privacy breaches are a potential ethical concern, as research regarding energy and emissions may include sensitive information about individuals. However, our data does not include such metrics. It focuses on countries and industries, opposed to individuals so this is not a concern. It is also important to know that bias in data collection could pose ethical concern. Although, to our knowledge Sam Donald does not have any vested interests or ties to certain organizations or companies that would skew the data.

Literature Review: Find one published credible article on the topic you are interested in researching. https://ecowarriorprincess.net/2018/04/carbon-intensive-industries-industry-sectors-emit-the-most-carbon/ Provide a one paragraph summary about the article. CO2 is by far one of the most harmful greenhouse gasses emitted that humans have increased. The article cites how "human activity is responsible for adding as much as 110.5 million tons of carbon dioxide daily into the atmosphere" from various industries. The article explains how the top 5 most carbon intensive industries are energy production, agriculture, industry, transport, and residential sector. It also explains how in different parts of the world these industries vary in degree of carbon production. Energy production to power homes, offices, etc from fossil fuels adds greatly to CO2 production. The article discusses the global distribution by sector and how it depends on coal, natural gas, and oil but not how they differ independently. In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

Our research question is different than the article cited because our research question aspires to split up the industries as well as three countries in three different stages of development to then explore which country adds the most or least to CO2 emissions by which industry. Essentially, we seek to explore with more specificity which industries depending on the stage of development of the country add to CO2 emissions instead of only in a global point of view that the article does.

Sources:

https://rhg.com/research/chinas-emissions-surpass-developed-countries/

https://www.un.org/en/climatechange/science/causes-effects-climate-change#:\~:text=Fossil%20fuels%20%E2%80%93%20coal%2C%20oil%20and,they%20trap%20the%20sun's%20heat.

**- Methodology**

```{r}
library(tidyverse)
library(tidymodels)

global_emissions <- read_csv("data/global_emissions.csv")
```

```{r}
#| label: filter-data

target_emissions <- global_emissions |>
  filter(Country.Name %in% c("India", "United States", "China"))

```

```{r}
#| label: scatterplot-coal

target_emissions |>
  ggplot(
    aes(x = Year, 
        y = Emissions.Production.CO2.Coal,
        color = Country.Name)
    ) +
    labs(x = "Time (In Years)", 
       y =  "Emissions Production of Coal",
       title = "Emissions Production of Coal in Years",
       color = "Country") +
    geom_point() +
    geom_smooth(method = "lm" , se = F)

```

```{r}
#| label: scatterplot-coal-r^2

model_coal <- linear_reg() |>
  set_engine("lm") |>
  fit(Emissions.Production.CO2.Coal ~ Year * Country.Name, data = target_emissions)

```

```{r}
#| label: model_coal_predict_unitedstates

predict(model_coal, data.frame(Year = 2050, Country.Name = "United States"))

```

```{r}
#| label: model_coal_predict_india

predict(model_coal, data.frame(Year = 2050, Country.Name = "India"))

```

```{r}
#| label: model_coal_predict_china

predict(model_coal, data.frame(Year = 2050, Country.Name = "China"))

```

```{r}
#| label: scatterplot-gas

target_emissions |>
  ggplot(
    aes(x = Year, 
        y = Emissions.Production.CO2.Gas,
        color = Country.Name)
    ) +
    labs(x = "Time (In Years)", 
       y =  "Emissions Production of Gas",
       title = "Emissions Production of Gas in Years",
       color = "Country") +
    geom_point() +
    geom_smooth(method = "lm" , se = F)

```

```{r}
#| label: scatterplot-gas-r^2

model_gas <- linear_reg() |>
  set_engine("lm") |>
  fit(Emissions.Production.CO2.Gas ~ Year * Country.Name, data = target_emissions) 

```

```{r}
#| label: model_gas_predict_unitedstates

predict(model_gas, data.frame(Year = 2049, Country.Name = "United States"))

```
```{r}
#| label: model_gas_predict_india

predict(model_gas, data.frame(Year = 2050, Country.Name = "India"))

```

```{r}
#| label: model_gas_predict_china

predict(model_gas, data.frame(Year = 2050, Country.Name = "China"))

```

```{r}
#| label: scatterplot-oil

target_emissions |>
  ggplot(
    aes(x = Year, 
        y = Emissions.Production.CO2.Oil,
        color = Country.Name)
    ) +
    labs(x = "Time (In Years)", 
       y =  "Emissions Production of Oil",
       title = "Emissions Production of Oil in Years",
       color = "Country") +
    geom_point() +
    geom_smooth(method = "lm" , se = F)

```

```{r}
#| label: scatterplot-oil-r^2

model_oil <- linear_reg() |>
  set_engine("lm") |>
  fit(Emissions.Production.CO2.Oil ~ Year * Country.Name, data = target_emissions)

```

```{r}
#| label: model_oil_predict_unitedstates

predict(model_oil, data.frame(Year = 2050, Country.Name = "United States"))

```
```{r}
#| label: model_oil_predict_india

predict(model_oil, data.frame(Year = 2050, Country.Name = "India"))

```
```{r}
#| label: model_oil_predict_china

predict(model_oil, data.frame(Year = 2050, Country.Name = "China"))

```

```{r}
#| label: mean-coal

target_emissions |>
 group_by(Country.Name) |>
 summarise(mean_coal = mean(Emissions.Production.CO2.Coal))

```

```{r}
#| label: mean-gas

target_emissions |>
 group_by(Country.Name) |>
 summarise(mean_gas = mean(Emissions.Production.CO2.Gas))

```

```{r}
#| label: mean-oil

target_emissions |>
 group_by(Country.Name) |>
 summarise(mean_oil = mean(Emissions.Production.CO2.Oil))

```

**- Results**

The project explored coal, gas, and oil consumption by three countries - China, India, and the United States. These three countries are at three different points in their development and the data contributes to this point. For coal, China has the greatest consumption by a significant amount and this value continues to grow in recent time with over 6000 metric tons per capita. In the past, the United States has had more consumption than India but in recent years, they have flipped in consumption level. Now, the United States has reduced its consumption of coal and is slightly under India's consumption at around 1000 metric tons per capita.

For gas, the United States has the greatest consumption at over 2000 metric tons per capita. The United States was steady until 2010 and has in recent years continued to rise. The next greatest consumption of gas is China which is consistently growing over time and is currently around 500 metric tons per capita. India's consumption grew until 2010 and is slightly decreasing in recent years. India's consumption is around 125 metric tons per capita.

For oil, the United States has the greatest consumption but had a slight decline around 2005 but this level has again continued to rise after the decline. The United State's consumption is around 2500 metric tons per capita. China is the next highest around 1500 metric tons per capita and India's consumption is around 600 metric tons per capita.

The mean coal consumption for coal in China, India, and the United States respectively are 4651, 872, and 1923 metric tons per capita. The mean gas consumption for coal in China, India, and the United States respectively are 164, 71, and 1285 metric tons per capita. The mean oil consumption for coal in China, India, and the United States respectively are 871, 380, and 2328 metric tons per capita.

In general, India is growing the fastest in consumption for all three modes of energy. We suggest that the United States is a greater stage of development now to start using more alternative energy forms and renewable forms of energy. The slight steadiness in the trend lines of the United States support this idea along with the subtle declines present in coal and oil.
